---
title: "Sharpe Ratio with Julia"
subtitle: "Mathematical Programming with Julia"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    font_size: 20pts
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

<style type="text/css">
  body{
  font-size: 20pt;
}
</style>

```{r eval=FALSE,include=FALSE}

# CT6 
# - ASI 2005 April Question B - 1
# - ASI 2006 April Question B - 1

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(dplyr)
library(janitor)


```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  #base_color = "#4169e1", #)(vvv#TREES
  #background_color = "#E6E6FA",  #TREE
  base_color = "black", #)(
  background_color =  "#1dddd1",,
  text_color="black",
  text_bold_color = "black",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "400", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

### Sharpe Ratio




**Here's the formula:**

**Sharpe Ratio = (Rp - Rf) / σ**

* **Rp:** Portfolio return
* **Rf:** Risk-free rate of return (e.g., return on a short-term government bond)
* **σ:** Standard deviation of portfolio returns

---

**Interpretation:**

* **Higher Sharpe Ratio:** Indicates better risk-adjusted performance. This means the investment generates higher returns for a given level of risk (volatility).
* **Negative Sharpe Ratio:** Suggests the investment's returns are below the risk-free rate after adjusting for risk. 
* **Sharpe Ratio of 1 or higher:** Generally considered good. 
* **Sharpe Ratio of 2 or higher:** Often considered very good.

---

**Key Points:**

* **Risk-Adjusted Return:** The Sharpe Ratio focuses on how much excess return you receive for each additional unit of risk you take.
* **Volatility:** Standard deviation measures the volatility or fluctuation of returns. Higher volatility implies higher risk.
* **Comparison:** The Sharpe Ratio helps compare the performance of different investments or portfolios, even if they have different levels of risk.

**Example:**

* If a portfolio has an annual return of 12%, the risk-free rate is 3%, and the standard deviation of returns is 8%, the Sharpe Ratio would be: 
   (12% - 3%) / 8% = 0.9 

---

**Limitations:**

* **Assumes Normal Distribution:** The Sharpe Ratio assumes that returns are normally distributed, which may not always be the case in reality.
* **Focus on Total Volatility:** It considers both upside and downside volatility, while some investors may be more concerned with downside risk only.

**In Summary:**

The Sharpe Ratio is a valuable tool for evaluating the risk-adjusted performance of investments and portfolios. By considering both return and risk, it helps investors make more informed investment decisions.

---

```julia
function calculate_sharpe_ratio(returns, risk_free_rate)
    """
    Calculates the Sharpe Ratio for a given series of returns.

    Args:
        returns: A vector of returns.
        risk_free_rate: The risk-free rate of return.

    Returns:
        The Sharpe Ratio.
    """

    avg_return = mean(returns)
    std_dev = std(returns)

    sharpe_ratio = (avg_return - risk_free_rate) / std_dev

    return sharpe_ratio
end

# Example usage:
returns = [0.02, -0.01, 0.03, -0.02, 0.01]
risk_free_rate = 0.01

sharpe_ratio = calculate_sharpe_ratio(returns, risk_free_rate)
println("Sharpe Ratio:", sharpe_ratio)
```

---

**Explanation:**

**1**. **Function Definition:**
   - `calculate_sharpe_ratio(returns, risk_free_rate)`: Defines the function with two arguments:
     - `returns`: A vector containing the series of returns.
     - `risk_free_rate`: The risk-free rate of return.

**2**. **Calculate Average Return:**
   - `avg_return = mean(returns)`: Calculates the average return of the given series of returns using the `mean()` function.

**3**. **Calculate Standard Deviation:**
   - `std_dev = std(returns)`: Calculates the standard deviation of the returns using the `std()` function.

**4**. **Calculate Sharpe Ratio:**
   - `sharpe_ratio = (avg_return - risk_free_rate) / std_dev`: Calculates the Sharpe Ratio by dividing the excess return (average return minus risk-free rate) by the standard deviation.

---

**5**. **Return Sharpe Ratio:**
   - `return sharpe_ratio`: Returns the calculated Sharpe Ratio.

**6**. **Example Usage:**
   - `returns = [0.02, -0.01, 0.03, -0.02, 0.01]`: Creates a vector containing sample return data.
   - `risk_free_rate = 0.01`: Sets the risk-free rate.
   - `sharpe_ratio = calculate_sharpe_ratio(returns, risk_free_rate)`: Calls the function to calculate the Sharpe Ratio.
   - `println("Sharpe Ratio:", sharpe_ratio)`: Prints the calculated Sharpe Ratio to the console.

This Julia script provides a concise and efficient way to calculate the Sharpe Ratio.

