---
title: "Data Science With Julia"
output:
  flexdashboard::flex_dashboard:
    theme: 
      version: 4
      bootswatch: minty
---

```{r  include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


About {data-navmenu="About"}
=====================================

Column {.tabset}
--------------------

### Data Science with Julia

#### Data Science with Julia

**Week 1: Introduction to Julia and Data Science**
- Overview of Data Science
- Why Julia for Data Science?
- Setting Up Julia Environment
- Basic Syntax and Data Types
- Simple Data Manipulation

**Week 2: Julia Fundamentals**
- Control Flow (loops, conditions)
- Functions and Modules
- Working with Arrays and Matrices
- Introduction to DataFrames.jl

**Week 3: Data Manipulation**
- Loading and Saving Data
- Data Cleaning and Preprocessing
- Handling Missing Data
- Data Transformation and Aggregation

**Week 4: Exploratory Data Analysis (EDA)**
- Descriptive Statistics
- Data Visualization with Plots.jl
- Advanced Plotting Techniques
- Correlation Analysis

**Week 5: Probability and Statistics**
- Introduction to Probability
- Common Probability Distributions
- Statistical Tests and Inference
- Resampling Methods

**Week 6: Linear Algebra for Data Science**
- Vectors and Matrices
- Matrix Operations
- Eigenvalues and Eigenvectors
- Singular Value Decomposition

**Week 7: Regression Analysis**
- Simple Linear Regression
- Multiple Linear Regression
- Diagnostics and Model Assumptions
- Polynomial Regression

**Week 8: Classification Techniques**
- Logistic Regression
- Decision Trees
- Support Vector Machines
- Model Evaluation Metrics

**Week 9: Unsupervised Learning**
- Clustering Algorithms (K-Means, Hierarchical Clustering)
- Dimensionality Reduction (PCA, LDA)
- Association Rule Mining

**Week 10: Time Series Analysis**
- Introduction to Time Series Data
- Time Series Decomposition
- Forecasting Models (ARIMA, Exponential Smoothing)
- Evaluating Forecast Accuracy

**Week 11: Natural Language Processing (NLP)**
- Text Preprocessing and Tokenization
- Sentiment Analysis
- Topic Modeling
- Word Embeddings

**Week 12: Neural Networks and Deep Learning**
- Introduction to Neural Networks
- Building Neural Networks with Flux.jl
- Training and Evaluating Models
- Convolutional Neural Networks (CNNs)

**Week 13: Big Data with Julia**
- Introduction to Big Data
- Working with Distributed Computing
- Julia and Apache Spark
- Case Studies

**Week 14: Advanced Topics in Data Science**
- Model Deployment and Productionization
- Model Interpretation and Explainability
- Ethical Considerations in Data Science
- Latest Trends and Research in Data Science

**Week 15: Capstone Project**
- Project Planning and Data Collection
- Applying Data Science Techniques
- Project Presentation and Evaluation


### MlJ Julia package

```{r child = "MLJ_Julia_Package.Rmd"}
```