---
title: "Random Simulation with Julia"
output:
  flexdashboard::flex_dashboard:
    theme: 
      version: 4
      bootswatch: minty
---

```{r  include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


About {data-navmenu="About"}
=====================================

Column {.tabset}
--------------------

### Syllabus

```{r child = "Sampling_Random_Numbers_Julia_Syllabus.Rmd"}

```

### Resources

#### Random Number Generation, Sampling, and Simulation with Julia:


----------------------------------------

Random Number Generation, Sampling, and Simulation with Julia https://rpubs.com/JuliaWorkshop/Sampling_Random_Numbers_Julia_Syllabus

Simulating Exponential Random Variate using Julia https://rpubs.com/JuliaWorkshop/Exponential_Simulation_Julia
https://rpubs.com/JuliaWorkshop/Binomial_Simulation_Julia

-------------------------------------------------------

* [The Random.jl package in Julia](https://rpubs.com/JuliaWorkshop/Random_Julia_Package)

* [The Law of Large Numbers (LLN)](https://rpubs.com/JuliaWorkshop/Law_Large_Numbers_Julia)

* [Markov Chain Monte Carlo (MCMC)](https://rpubs.com/JuliaWorkshop/MCMC_Lesson_Plan_Julia)

* [Implementing Metropolis-Hastings in Julia](https://rpubs.com/JuliaWorkshop/Metropolis_Hastings_Julia)


Week 1:  {data-navmenu="Components"}
=====================================

Column {.tabset}
--------------------

### Week 1



```{r child = "Sampling_Functions.Rmd"}
```

```{r child = "Components/Exponential_Simulation_Julia.Rmd"}
```



Week 2  {data-navmenu="Components"}
=====================================

Column {.tabset}
--------------------

### Week 2

```{r child = "Components/Bootstrap_Sampling_Julia.Rmd"}
```




Week 5:  {data-navmenu="Components"}
=====================================

Column {.tabset}
--------------------

### Week 5

* [Monte Carlo Simulation in Julia (Week 5 Lesson Plan)](https://rpubs.com/JuliaWorkshop/Monte_Carlo_Simulation_Lesson_Plan_Julia)

https://rpubs.com/JuliaWorkshop/Markov_Chains_Julia_Tutorial
https://rpubs.com/JuliaWorkshop/Markov_Chain_Example_Julia


Week 6:  {data-navmenu="Components"}
=====================================

Column {.tabset}
--------------------


```{r child = "Components/Markov_Chains_Julia.Rmd"}

```


Week 10  {data-navmenu="Components"}
=====================================

Column {.tabset}
--------------------

### Week 10

```{r child = "Components/Numerical_Integration.Rmd"}
```


Week 11  {data-navmenu="Advanced Topics"}
=====================================

Column {.tabset}
--------------------

### Week 11


<p>


```{r child = "Components/Box_Muller_Transform_Method.Rmd"}
```



Week 12  {data-navmenu="Advanced Topics"}
====================================

Column {.tabset}
--------------------

### Week 12

Advanced Topics

```{r child = "Components/Turing_Julia_Package.Rmd"}
```

